Sumbission Steps

### 2020-10-06 code/03-submission-steps.Rmd
changed readme to uppercase in data folder

    # Create a vector with code and data files to be included for submission 
    data_files <-
      c(
        "../data/readme.txt",
        "../data/bullet-test.csv.zip",
        "../data/bullet-train.csv.zip",
        "../data/example-signatures.csv.zip"
      )

>>>>

    # Create a vector with code and data files to be included for submission 
    data_files <-
      c(
        "../data/README.txt",
        "../data/bullet-test.csv.zip",
        "../data/bullet-train.csv.zip",
        "../data/example-signatures.csv.zip"
      )
